\bf Title

### 2023-10-05 article/paper_padic_spec.tex
commit by Simone
first par

\newcommand{\R}{\mathbb{R}} % real numbers
\newcommand{\C}{\mathbb{C}} % complex numbers
\newcommand{\N}{\mathbb{N}} % integers

@@

\footnotetext[1]{ENS Paris-Saclay, Université Paris-Saclay.}
\footnotetext[2]{Université de Limoges, CNRS, XLIM, Limoges, France.}

@@

\section{Introduction}
\subsection{Motivations and main results}
\subsection{Real spectrahedra}

@@

>>>>

\newcommand{\R}{\mathbb{R}} % real numbers
\newcommand{\C}{\mathbb{C}} % complex numbers
\newcommand{\N}{\mathbb{N}} % integers
\newcommand{\sym}{\mathbb{S}} % matrices symétriques

@@

\footnotetext[1]{ENS Paris-Saclay, Université Paris-Saclay, France.}
\footnotetext[2]{Université de Limoges, CNRS, XLIM, Limoges, France.}

@@

\section{Introduction}
\subsection{Motivations and main results}

il faudra mentionner (et peut être motiver l'approche p-adique) :
\begin{itemize}
\item les questions ouvertes de complexité concernant la programmation semidefinie (pas clair si NP $\cap$ co-NP
  dans le modele de Turing)
\item les questions ouvertes géométriques (Conjecture de Lax)
\end{itemize}

\subsection{Real spectrahedra}

Let $\sym_m(\R)$ be the vector space of $m \times m$ real symmetric matrices. We recall that
a matrix $M \in \sym_m(\R)$ is called positive semidefinite ($M \succeq 0$) whenever the quadratic
form $x \mapsto x^TMx$ is globally nonnegative. Recall that by the Spectral Theorem, $M \succeq 0$
if and only if the eigenvalues of $M$ are nonnegative, if and only if all the principal minors of
$M$ are nonnegative. The set of positive semidefinite matrices, denoted $\sym_m^+(\R) \subset \sym_m(\R)$,
is a closed convex cone with non-empty interior in $\sym_m(\R)$.

A {\it (real) spectrahedron} is an affine slice of the

@@

\section{Linear matrix inequalities}
